---
title: "STAT40830 Homework - 01"
author: "Kavi Priya Mathimaran"
format: html
editor: visual
---

## Home Work 01

Advance Data Programming with R - Online STAT40830

### *Introduction*

*AIRQUALITY IN NEW YORK DURING 1973*

The airquality dataset is a built-in R dataset that contains daily air quality measurements in New York from May to September 1973. It includes variables like temperature, wind speed, solar radiation, and ozone levels.

```{r}
#| echo: false
# Load required dataset
data("airquality")
# Remove rows with missing values for plotting
data <- na.omit(airquality)
# View first few rows of the dataset
head(airquality)
```

### *Plotting*

```{r}
#| echo: false
# Scatterplot of Ozone vs Temperature
plot(data$Temp, data$Ozone,
     main = "Ozone Levels vs Temperature",
     xlab = "Temperature (°F)",
     ylab = "Ozone (ppb)",
     pch = 19,
     col = "purple")
```

#### *Description*

This scatter-plot shows the relationship between the temperature and the ozone levels:

-   The x-axis represents temperature in Fahrenheit (F).

-   The y-axis shows ozone concentration in parts per billion (ppb).

-   Each dot in the plot corresponds to a day’s recorded values.

From the plot, we observe that higher temperatures tend to be associated with higher ozone levels, though there is variation due to other environmental factors.
